Summary of tumor cell classification with `SingleR` for `r params$library_id`

### 2024-07-23 analyses/cell-type-ewings/template_notebooks/singler-workflow/01-singler-results.Rmd
use patchwork

```{r}
geneset_columns |> 
  purrr::map(\(column){
    plot_density(classification_df,
                 column,
                 "singler_tumor_normal")
  })
```

@@

```{r}
marker_gene_columns |> 
  purrr::map(\(column){
    plot_density(classification_df,
                 column,
                 "singler_lumped")
  })
```

@@

```{r}
geneset_columns |> 
  purrr::map(\(column){
    plot_density(classification_df,
                 column,
                 "singler_lumped")
  })
```

@@

```{r}
geneset_columns |> 
  purrr::map(\(column){
    plot_density(classification_df,
                 column,
                 "consensus")
  })
```

>>>>

```{r, fig.height=10}
geneset_columns |> 
  purrr::map(\(column){
    plot_density(classification_df,
                 column,
                 "singler_tumor_normal")
  }) |> 
  patchwork::wrap_plots(ncol = 1)
```

@@

```{r, fig.height=10}
marker_gene_columns |> 
  purrr::map(\(column){
    plot_density(classification_df,
                 column,
                 "singler_lumped")
  }) |> 
  patchwork::wrap_plots(ncol = 1)
```

@@

```{r, fig.height=10}
geneset_columns |> 
  purrr::map(\(column){
    plot_density(classification_df,
                 column,
                 "singler_lumped")
  }) |> 
  patchwork::wrap_plots(ncol = 1)
```

@@

```{r, fig.height=10}
geneset_columns |> 
  purrr::map(\(column){
    plot_density(classification_df,
                 column,
                 "consensus")
  }) |> 
  patchwork::wrap_plots(ncol = 1)
```
